\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}. The idea was to to study the effects of heterogeneity of a quadrant model geometry using the current element type. This, in large scale, is a problem that can be found in petroleum production operations. \red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}

\medskip
%Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
The flow profile follows the same behaviour with the experimental work of \citet{evans_1994}. In both cases the flow will not follow the standar source-sink behaviour while the mobility ratio (or VR) is playing a crucial role for these flows. The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow.

>>>>

\medskip
Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1. They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions. Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.

\medskip
%Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
\red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
The flow profile follows the same behaviour with the experimental work of \citet{evans_1994}. In both cases the flow will not follow the standar source-sink behaviour while the mobility ratio (or VR) is playing a crucial role for these flows. The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow.
